%-----------------------------------------------------------------------------------------------------------------------------------------------%
%	The MIT License (MIT)
%
%	Copyright (c) 2021 Jitin Nair
%
%	Permission is hereby granted, free of charge, to any person obtaining a copy
%	of this software and associated documentation files (the "Software"), to deal
%	in the Software without restriction, including without limitation the rights
%	to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%	copies of the Software, and to permit persons to whom the Software is
%	furnished to do so, subject to the following conditions:
%	
%	THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%	IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%	FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%	AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%	LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%	OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
%	THE SOFTWARE.
%	
%
%-----------------------------------------------------------------------------------------------------------------------------------------------%

%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

% article class because we want to fully customize the page and not use a cv template
\documentclass[a4paper,10pt]{article} % set font size to be between 10 and 12

%----------------------------------------------------------------------------------------
%	FONT
%----------------------------------------------------------------------------------------

% % fontspec allows you to use TTF/OTF fonts directly
% \usepackage{fontspec}
% \defaultfontfeatures{Ligatures=TeX}

% % modified for ShareLaTeX use
% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
%\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}

%debug page outer frames
%\usepackage{showframe}


% job listing environments
\newenvironment{jobshort}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    }
    {
    }

\newenvironment{joblong}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    \begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt,label=--]
    }
    {
    \end{itemize}
    \end{minipage}    
    }



%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

% \begin{tabularx}{\linewidth}{ @{}X X@{} }
% \huge{Your Name}\vspace{2pt} & \hfill \emoji{incoming-envelope} email@email.com \\
% \raisebox{-0.05\height}\faGithub\ username \ | \
% \raisebox{-0.00\height}\faLinkedin\ username \ | \ \raisebox{-0.05\height}\faGlobe \ mysite.com  & \hfill \emoji{calling} number
% \end{tabularx}

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Kimberly Prijadi} \\[7.5pt]
\href{https://github.com/frtheatelier}{\raisebox{-0.05\height}\faGithub\ frtheatelier} \ $|$ \ 
\href{https://linkedin.com/in/kimberlyprijadi}{\raisebox{-0.05\height}\faLinkedin\ kimberlyprijadi} \ $|$ \ 
% \href{https://mysite.com}{\raisebox{-0.05\height}\faGlobe \ mysite.com} \ $|$ \ 
\href{mailto:prijadikimberly@gmail.com}{\raisebox{-0.05\height}\faEnvelope \ prijadikimberly@gmail.com} \ $|$ \ 
\href{tel:+14377341859}{\raisebox{-0.05\height}\faMobile \ +1 (437) 734-1859} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
% EXPERIENCE SECTIONS
%----------------------------------------------------------------------------------------

%Interests/ Keywords/ Summary
\section{Summary}
I am a computer science student with a deep love for design and development. My main strengths lie in web design and development, and I seek opportunities to create interesting projects and develop my skills in frontend/backend development.

%Experience
% \section{Work Experience}

% \begin{jobshort}{Designation}{Jan 2021 - present}
% long long line of blah blah that will wrap when the table fills the column width long long line of blah blah that will wrap when the table fills the column width long long line of blah blah that will wrap when the table fills the column width long long line of blah blah that will wrap when the table fills the column width
% \end{jobshort}


% \begin{joblong}{Designation}{Mar 2019 - Jan 2021}
% \item long long line of blah blah that will wrap when the table fills the column width
% \item again, long long line of blah blah that will wrap when the table fills the column width but this time even more long long line of blah blah. again, long long line of blah blah that will wrap when the table fills the column width but this time even more long long line of blah blah
% \end{joblong}

%----------------------------------------------------------------------------------------
%	Qualifications
%----------------------------------------------------------------------------------------
\section{Qualifications}
\begin{itemize}
    \item Second-year student in the Computer Science Specialist program, also majoring in Mathematics and minoring in Philosophy at the University of Toronto
    \item Excellent collaborative skills, demonstrated through a team hackathon project "Capybara Bash" and as an event planner of the event "Nourish and Recharge: Decorate a Tote-bag Over Lunch".
    \item ~2 years in community engagement and leadership, particularly as a tour guide and mentor.
    \item Solid understanding in HTML, CSS, and Javascript, showcased by a number of front-end side projects.
    \item Practical back-end knowledge using PHP and MySQL, including building systems with user authentication and CRUD functionality.
    \item Experience in rapid prototyping and game development using Godot 4.3 and JavaScript, showcasing teamwork and problem-solving in fast-paced environments.
\end{itemize}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{tabularx}{\linewidth}{@{}l X@{}}
    2024 - present & Honors Bachelor of Science at \textbf{University of Toronto} \hfill \normalsize (GPA: 3.84/4.0) \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------
%\section{Skills}
%\begin{tabularx}{\linewidth}{@{}l X@{}}
%    Proficient &  \normalsize{Python, HTML, CSS, JavaScript, PHP, MySQL}\\
%    Familiar  &  \normalsize{C++, GoLang, Laravel, Vue.js, Swift UI, Godot (GDScript)}\\
%    Other  &  \normalsize{UI/UX design}\\
%\end{tabularx}
  
%Projects
\section{Projects}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Personal site} & \hfill \href{https://frtheatelier.github.io/dashboard/}{Link to Page} \\[3.75pt]
\multicolumn{2}{@{}X@{}}{
    Created a personal website with a clean and creative user interface using HTML, CSS, and Javascript to showcase various artistic works and programming projects
}  \\
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Aléatoire: Varied Web Apps} & \hfill \href{https://frtheatelier.github.io/aleatoire/}{Link to Hub} \\[3.75pt]
\multicolumn{2}{@{}X@{}}{
    \begin{itemize}
        \item Built multiple web apps using JavaScript, jQuery, Vue, and Ajax to explore front-end technologies, including a calculator and Wikipedia article generator.
        \item Created a math-based web tool to identify perfect numbers and their factors, enhancing user engagement with number theory.
        \item Developed an interactive Caesar Cipher mini-game applying cryptographic concepts through JavaScript logic.
    \end{itemize}
}  \\
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Restaurant menu and booking portal} & \hfill \href{https://puedeeducation.com/kimresto/index.php}{Link to Demo}\footnote{Demo login: username \texttt{vani}, password \texttt{12345}. No real data; for demonstration purposes only.} \\[3.75pt]
\multicolumn{2}{@{}X@{}}{
    Developed a restaurant menu and booking system with login, CRUD functionality, and Bootstrap styling using PHP and MySQL as part of a web development course project; successfully published on the course website.
}  \\
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Capybara Bash} & \hfill \href{https://github.com/harshshriv8man/Capybara-Bash-Game}{Link to Prototype} \\[3.75pt]
\multicolumn{2}{@{}X@{}}{
    Collaborated in a team of three to design and develop a visually engaging 2D platformer game prototype featuring a capybara and moving platforms using Godot 4.3 to be presented to judges at IEEE's NewHacks 2024
}  \\
\end{tabularx}

%Course Projects
\section{Course Projects}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{"Where are my Items": a text-based adventure game} & \hfill \\[3.75pt]
\multicolumn{2}{@{}X@{}}{
    \begin{itemize}
        \item Developed a functional text-based adventure game in Python featuring three minigames, one puzzle, two easter-eggs, and additional interactive elements using appropriate data structures and coding practices
        \item Authored comprehensive documentation including a game walkthrough, item and puzzle descriptions, and a reflective analysis of challenges and puzzle complexity
    \end{itemize}
}  \\
\end{tabularx}

%Activities
\section{Activities}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Fall Campus Day Tour Guide} & Oct 2024\hfill \\[3.75pt]
\multicolumn{2}{@{}X@{}}{
    Led tours for groups of 10+ prospective students and families around the Bahen Centre, sharing insights on first-year courses and student life while encouraging engagement; consistently delivered on-time tours and received positive feedback from participants.
}  \\
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Event Coordinator} & Nov 2024 - Mar 2025\hfill \\[3.75pt]
\multicolumn{2}{@{}X@{}}{
    \begin{itemize}
        \item Organized and co-hosted "Nourish and Recharge: Decorate a Tote-bag Over Lunch" in collaboration with UofT’s Center of International Experience, successfully engaging ~40 attendees
        \item Planned and delivered a short presentation on self-care and study strategies, fostering a warm and welcoming event atmosphere.
    \end{itemize}
}  \\
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{CSSU Orientation Leader} & Sep 2025\hfill \\[3.75pt]
\multicolumn{2}{@{}X@{}}{
    \begin{itemize}
        \item Led a scavenger hunt guiding 6 students, fostering engagement through collaborative poster design activities and finished in 3rd place.
        \item Provided informative answers about course activities and opportunities, enhancing first-year students’ orientation experience.
    \end{itemize}
}  \\
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{PERMIKATO X VIP Toronto Buddy} & Sep 2025 - present\hfill \\[3.75pt]
\multicolumn{2}{@{}X@{}}{
    \begin{itemize}
        \item Mentored 2 first-year UofT students, initiating conversations and offering guidance on local resources and social events.
        \item Answered questions about program applications and university life to support mentees’ transition.
    \end{itemize}
}  \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	PUBLICATIONS
%----------------------------------------------------------------------------------------
% \section{Publications}
% \begin{refsection}[citations.bib]
% \nocite{*}
% \printbibliography[heading=none]
% \end{refsection}

\vfill
\center{\footnotesize Last updated: \today}

\end{document}
